Drones in Wind

### 2017-08-30 Papers/main.tex

\end{lstlisting}
\end{quote}
\clearpage
The Moment and rotation matrices are then:
\begin{quote}
\begin{lstlisting}
I = [Ix 0 0; 0 Iy 0; 0 0 Iz];
Rw = [1 0 -sin(theta); 
           0 cos(phi) cos(theta)*sin(phi); 
           0 -sin(phi) cos(theta)*cos(phi)];

@@

The new problem bounds are shown in table \ref{Problem Bounds} below:

@@

\subsubsection{Cost Function}
Using a cost function, an optimized trajectory around any aspect of the simulation can be found. The cost functions available for different variables are shown below. 
\textcolor{red}{Didn't update the cost functions, lazy}
\begin{quote}
\begin{lstlisting}
% Input:
problem.func.pathObj = @(t,x,u)( sum(u.^2,1) );

% Thrust:
problem.func.pathObj = @(t,x,u)( sum(u(2,:).^2,1) );

% Pitch Rate:
problem.func.pathObj = @(t,x,u)( sum(u(1,:).^2,1) );

% Time
problem.func.pathObj = @(t,x,u)( sum((x(1,:)-x_f).^2,1) 
                                +sum((x(3,:)-z_f).^2,1))

@@

\end{lstlisting}
\end{quote}
For our purposes, we explicitly used the "Time objective function for boundary points" and the other cost functions were commented out.

@@

usim = [controllerdata.actuators.f1; 
        controllerdata.actuators.f2;
        controllerdata.actuators.f3;
        controllerdata.actuators.f4];
\end{lstlisting}
\end{quote}
The preceding lines of code are meant to show how easily the data can be unpacked and plotted against each other. Below, Figure \ref{State Plot} shows the optimal and actual state of the quadrotor, and Figure \ref{Input Plot} shows the optimal and actual inputs of the quadrotor.
\newline
\newline

@@

\begin{itemize}
  \item \sout{Implement 3D rigid body dynamics}
  \item \sout{Implement additional aerodynamic forces such as drag and ground effect}
\end{itemize}
\textit{Controlling of an Single Drone}\cite{Controlling of an Single Drone} provides an outline for how to linearize a 3D quadcopter using rigid body dynamics. A key difference to note is that in the dynamics discussed in {\cite{Controlling of an Single Drone}, each of the four quadrotor blades can produce its own thrust, which will then control the pitch, roll, and yaw of the rigid body. Additionally, the paper gives a brief description of the mechanism on applying aerodynamic forces, namely, drag.}
\newline
\newline
\textit{Quadcopter Dynamics, Simulation, and Control}\cite{QDSC} provides the outline as to how we managed to redo the dynamics model. It also gives us step by step processes  \textcolor{red}{(outlined a bit by Michael) as to how to control the power and blahh blahh blahh}

>>>>

\end{lstlisting}
\end{quote}
\clearpage
The moment and rotation matrices are then:
\begin{quote}
\begin{lstlisting}
I = [Ix 0 0; 0 Iy 0; 0 0 Iz];
Rw = [1 0 -sin(theta); 
           0 cos(phi) cos(theta)*sin(phi); 
           0 -sin(phi) cos(theta)*cos(phi)];

@@

The new problem bounds are derived from the D'Andrea paper but have been adapted to the current model.  Namely, the thrust values now reflect the per-rotor thrust instead of the total.  They are shown in table \ref{Problem Bounds} below:

@@

\subsubsection{Cost Function}
Using a cost function, an optimized trajectory around any aspect of the simulation can be found. The time optimal cost function is shown below.
\begin{quote}
\begin{lstlisting}

@@

@@

usim = [controllerdata.actuators.f1; 
        controllerdata.actuators.f2;
        controllerdata.actuators.f3;
        controllerdata.actuators.f4];
\end{lstlisting}
\end{quote}
The preceding lines of code are meant to show how easily the data can be unpacked and plotted against each other. The below figures show the trajectory and simulated states and inputs of the quadrotor for varying goal positions.
\newline
\newline

@@

\begin{itemize}
  \item \sout{Implement 3D rigid body dynamics}
  \item \sout{Implement additional aerodynamic forces such as drag and ground effect}
\end{itemize}
\textit{Controlling of an Single Drone}\cite{Controlling of an Single Drone} provides an outline for how to linearize a 3D quadcopter using rigid body dynamics. A key difference to note is that in the dynamics discussed in {\cite{Controlling of an Single Drone}, each of the four quadrotor blades can produce its own thrust, which will then control the pitch, roll, and yaw of the rigid body. Additionally, the paper gives a brief description of the mechanism on applying aerodynamic forces, namely, drag.}
\newline
\newline
\textit{Quadcopter Dynamics, Simulation, and Control}\cite{QDSC} provides the outline as to how we managed to redo the dynamics model. It also gives us step-by-step processes on creating a relationship between voltage drop across a motor and the thrust produced by the respective propeller.  Modelling our control inputs as voltage drops instead of thrusts is a more accurate description of what we will have access to on an actual vehicle, and may serve as preperation for writing flight code.
